### 2023-09-13 doc/_single_results.qmd
fixing fig legend

![**Single dataset inference**. (A) Frequency trajectories that represent the
raw data going into the inference. (B) Log frequency ratio between two adjacent
time points used by the inference pipeline. Darker lines represent the neutral
barcodes. These transformed data are much more noisy than the
seemingly smooth frequency trajectories. (B) Examples of the posterior
predictive checks for all neutral lineages (upper left panel) and a subset of
representative mutant lineages. Error bars represent the 68\% credible region on
the mutant relative fitness marginal distribution. (C) Comparison between the
ground truth fitness value from the logistic-growth simulation and the inferred
fitness value. Gray error bars represent the 68\% posterior credible region. (D)
The empirical cumulative distribution function (ECDF) for the absolute z-score
value of the ground truth parameter value within the inferred fitness
posterior distribution.](./figs/fig02){#fig-02}

>>>>

![**Single dataset inference**. (A) Frequency trajectories that represent the
raw data going into the inference. (B) Log frequency ratio between two adjacent
time points used by the inference pipeline. Darker lines represent the neutral
barcodes. These transformed data are much more noisy than the seemingly smooth
frequency trajectories. (B) Examples of the posterior predictive checks for all
neutral lineages (upper left panel) and a subset of representative mutant
lineages. Shaded regions represent the 95\%, 68\%, and 5\% credible regions for
the data. The reported errors above the plot represent the 68\% credible region
on the mutant relative fitness marginal distribution. (C) Comparison between the
ground truth fitness value from the logistic-growth simulation and the inferred
fitness value. Gray error bars represent the 68\% posterior credible region. (D)
The empirical cumulative distribution function (ECDF) for the absolute z-score
value of the ground truth parameter value within the inferred fitness posterior
distribution.](./figs/fig02){#fig-02}
